Effects of the body force on the evacuation dynamics

### 2020-02-04 paper.tex
arregle la figura de los triangulos y mejore una parte de resultados

In the same way as with the bottleneck geometry, we computed the contact network to study the topological differences that arise from increasing the $k_n$ value. Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values. When the density is low,  the degree is zero because the pedestrians do not touch each other. When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree. As the density increases, the mean degree increases too until reaching an asymptotic behavior in degree six. Degree six, corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\

It is important to notice that in Fig. \ref{degree_dens} for a given value of density, the stiffer the pedestrians, the higher the degree. In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.\\

The mean overlap increases as the global density increases (see Fig. \ref{overlap_dens}) and the higher the stiffness the lower the overlap. This result is similar to the overlap vs. desired velocity obtained for bottleneck geometry. The higher the value of $k_n$ the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\

@@

As was mentioned above, increasing the $k_n$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in the bottleneck and corridor). Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor. Fig.~\ref{network_corridor} it shows the contact network corresponding to the corridor at a particular timestep and a particular global density. Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5. This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity). Notice that there are many more pedestrians with degree 6 in the case of $k_n=1.2$~E5 than the case of $k_n=0$. \\

This result is exactly the opposite of what we get in the bottleneck. This happens because, in the corridor, the lateral walls act like containers that force the pedestrian to increase their contacts. Whereas in the bottleneck there are no lateral walls. Thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree). \\

@@

In the corridor geometry, the crowd gets more connected if the pedestrians become stiffer. We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian. We found that a good descriptor to exhibit the connectivity is the number of triangles per node. A triangle is defined as a structure composed of three nodes all in contact with each other. Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k_n$. This descriptor allows to distinguish states with the same global density but different stiffness levels. In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree. \\

This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness. While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013} Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\

@@

The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry. Fig.~\ref{kn_vs_vx_corridor} shows the velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels. $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry. There is little to no change in the speed from zero to $k_n=$1.2~E4, from this value on, the diminishing of velocity is more abrupt.\\

The reason why the velocity reduces as the stiffness of the pedestrians' increases is that it becomes harder for pedestrians to walk forward. The difficulty arises because the pedestrian feels a much higher repulsion from the pedestrian ahead (due to the body force increment). Thus, they have no other option than moving at (almost) the same speed as the pedestrians that they have at their sides. This microscopic mechanism explains the macroscopic behavior of the crowd that turns the crowd from a fluid-like state into a solid-like state. When the stiffness is high enough (say $k_n=$1.2~E6), all the pedestrians walk at the same velocity. The pedestrians that walk in physical contact with the wall are the ones who determine the velocity of the whole crowd.\\

@@

The value of $k_n$ affects the velocity all along the corridor. Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs. the longitudinal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe). As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\

>>>>

In the same way as with the bottleneck geometry, we computed the contact network to study the topological differences that arise from increasing the $k_n$ value. Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values. When the density is low,  the degree is zero because the pedestrians do not touch each other. When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree. As the density increases, the mean degree increases until reaching an asymptotic behavior as approaching degree six. Degree six corresponds to the densest packing possible for identical hard circles; the result is a hexagonal packing arrangement.\\

It is important to notice that in Fig. \ref{degree_dens}, for a given value of density, the stiffer the pedestrians, the higher the degree. In the bottleneck geometry, the opposite thing happens. The stiffer the pedestrians, the lower the mean degree.
\\

The mean overlap increases as the global density increases (see Fig. \ref{overlap_dens}). For a given density, there is an inverse relation between stiffness and mean overlap. This result is similar to the overlap vs. desired velocity obtained for bottleneck geometry. The higher the value of $k_n$, the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting on the direction $n_{ij}$.\\

@@

As was mentioned above, increasing the $k_n$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in the bottleneck and corridor). Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor. Fig.~\ref{network_corridor} shows the contact network corresponding to the corridor at a particular timestep ($t=50$~s) and at a particular global density ($\rho=7$). Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5. This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity). Notice that there are many more pedestrians with degree 6 in the case of $k_n=1.2$~E5 than the case of $k_n=0$. \\

This result is exactly the opposite of what we get in the bottleneck geometry. This phenomenon occurs because, in the corridor, the lateral walls act like a containment barrier that forces the pedestrian to increase their contacts. Whereas in the bottleneck there are no lateral walls, thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree). \\

@@

In the corridor geometry, the crowd gets more connected if the pedestrians become stiffer. We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian. We found that a good descriptor to exhibit the connectivity is the number of triangles per node. A triangle is defined as a structure composed of three nodes, all in contact with each other. Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k_n$. This descriptor allows distinguishing states with the same global density but different stiffness levels. In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree. \\

This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometrical descriptors capable of properly describing granular systems with different stiffness levels. While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013}. Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\

@@

The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry. Fig.~\ref{kn_vs_vx_corridor} shows the mean velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels. $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry. There is little to no change in the speed from zero to $k_n=$1.2~E4, from this value on, the diminishing of velocity is more abrupt.\\

The reason why the velocity reduces as the stiffness of the pedestrians' increases is that it becomes harder for pedestrians to walk forward. The difficulty arises because the pedestrian feels a much higher repulsion from the pedestrian ahead (due to the body force increment). Thus, they have no choice but to move at (almost) the same speed as the individuals they have at their sides. This microscopic mechanism explains the macroscopic behavior that turns the crowd from a ``fluid-like state'' into a ``solid-like state''. When the stiffness is high enough (say $k_n=$1.2~E6), all the pedestrians walk at the same velocity. The pedestrians that walk in physical contact with the wall are the ones who determine the velocity of the whole crowd.\\

@@

The value of $k_n$ affects the velocity all along the corridor. Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs. the longitudinal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe). This behavior was observed in empirical measurements reported in Ref.~\cite{}. As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\
